Simple Type Theory is not too Simple

### 2021-04-06 article.tex
Update article

Moreover, one has the following results.

@@

Now, it suffices to teach Isabelle that a ring that is isomorphic to a local ring is local.

@@

To summarize, our work makes a triple contribution to Isabelle/HOL: a first stepping stone towards a new topology library, a second stepping stone towards a new algebra library and a formalization of schemes in algebraic geometry. Most importantly, our work demonstrates that intricate dependencies of algebraic structures can be managed elegantly in Isabelle. 

@@

Work on this paper was supported by the ERC Advanced Grant ALEXANDRIA (Project GA 742178).

>>>>

Moreover, one has the following result.

@@

Now, it suffices to teach Isabelle that a ring which is isomorphic to a local ring is local.

@@

To summarize, our work makes a triple contribution to Isabelle/HOL: a first stepping stone towards a new topology library, a second stepping stone towards a new algebra library and finally it develops a library for modern algebraic geometry. \\
Most importantly, our work meets the challenge of formalizing for the first time Grothendieck's schemes in a simple type theory and in doing so it demonstrates that intricate dependencies of algebraic structures can be managed elegantly in Isabelle. We hope this work will help mathematicians interested in the formalization of mathematics to make a more informed decision about which systems are available to them. \\

@@

Work on this paper was supported by the ERC Advanced Grant ALEXANDRIA (Project GA 742178).  \\
Anthony Bordg thanks Kevin Buzzard for his stimulating wit and his communicative energy.
